Three-Dimensional Fluorophore Orientation Imaging with Multiview Polarized Microscopy

### 2018-01-28 notes/2018-01-18-osa-abstract/abstract.tex
Finalizing osa abstract.

To reconstruct the orientation in each voxel we solved the following problem 
\begin{align}
\mathbf{f^{\thinspace *}}= \underset{\mathbf{f}\in\{\mathbf{e}_i\}\ i = 0,\dotsc,R}{\text{argmin}}
\ \ ||\thinspace\mathbf{g} - \Psi\hspace{0.1em}\mathbf{B}^+\mathbf{f}\thinspace||_2^2,
\end{align}
where $\mathbf{e}_i$ is a vector with a one in the $i$th entry and zeros
elsewhere. By constraining $\mathbf{f}$ we are assuming that all of the
fluorophores in each voxel are oriented in the same direction---a reasonable
assumption for this sample.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=16.cm, trim={0.1cm 1.3cm 0 0.5cm}]{figs/roi2/data.pdf}
  \caption{Fluorescence intensities of a small volume
    ($13.5\times 13.5\times 5.4\ \mu$m${}^3$) of a cell that was fixed, stained
    with Alexa Fluor 488 Phalloidin, and imaged in a dual-view microscope
    (diSPIM). The staining reveals two sets of actin bundles. Because
    fluorophores are aligned parallel to the bundles, their fluorescence
    intensities are modulated by the propagation direction and polarization of
    the excitation light. Bundles from bottom right to top left are highlighted
    for $x$-illumination and $z$-detection with
    $\phi_{\text{pol}} = 90^{\circ}$, while their intensities almost disappear
    for $z$-illumination and $x$-detection with $\phi_{\text{pol}} = 0^{\circ}$,
    which reveals the bundles running from bottom left to top right. The
    transfer functions at right use the normalized intensity value in each voxel
    to assign a color and opacity to each voxel.}
\end{figure}

\vspace{-1.22em}
\begin{minipage}{.263\textwidth}
  \includegraphics[width=3.7cm, trim={0cm 0cm 0 0cm}, right]{figs/roi2/recon_color.png}
\end{minipage}% This must go next to `\end{minipage}`
\begin{minipage}{.639\textwidth}
  Fig. 2. Reconstruction of fluorophore orientations based on all intensity
    data shown in Fig. 1. Orientations are shown as short lines only in voxels
    whose fluorescence intensities surpassed a threshold. To highlight the two
    sets of actin bundles discussed in the caption of Fig. 1, we split the
    volume with a plane and colored the proximal voxels red and the distal
    voxels green. The reconstructed orientations approximately align with the
    long axes of the actin filaments as expected.
\end{minipage}
 \vspace{-1em}
{\footnotesize\bibliography{abstract}{}}
\bibliographystyle{osajnl}

>>>>

To reconstruct the orientation in each voxel we solved the following problem 
\begin{align}
\mathbf{f^{\thinspace *}}= \underset{\mathbf{f}\in\{\mathbf{e}_i\}\ i = 0,\dotsc,R}{\text{argmin}}
\ \ ||\thinspace\mathbf{g} - \Psi\hspace{0.1em}\mathbf{B}^+\mathbf{f}\thinspace||_2^2,
\end{align}
where $\mathbf{e}_i$ is a vector with a one in the $i$th entry and zeros
elsewhere. By constraining $\mathbf{f}$ we are assuming that all of the
fluorophores in each voxel are oriented in the same direction---a reasonable
assumption for this sample.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=16.cm, trim={0.1cm 1.3cm 0 0.5cm}]{figs/roi2/data.pdf}
  \caption{Fluorescence intensities of a small volume
    ($13.5\times 13.5\times 5.4\ \mu$m${}^3$) of a cell that was fixed, stained
    with Alexa Fluor 488 Phalloidin, and imaged in a dual-view microscope
    (diSPIM). The staining reveals two sets of actin bundles. Because
    fluorophores are aligned parallel to the bundles, their fluorescence
    intensities are modulated by the propagation direction and polarization of
    the excitation light. Bundles from bottom right to top left are highlighted
    for $x$-illumination and $z$-detection with
    $\phi_{\text{pol}} = 90^{\circ}$, while their intensities almost disappear
    for $z$-illumination and $x$-detection with $\phi_{\text{pol}} = 0^{\circ}$,
    which reveals the bundles running from bottom left to top right.}
\end{figure}

\begin{minipage}{.263\textwidth}
  \includegraphics[width=3.7cm, trim={0cm 0cm 0 0cm}, right]{figs/roi2/recon_color-min.png}
\end{minipage}% This must go next to `\end{minipage}`
\begin{minipage}{.639\textwidth}
  Fig. 2. Reconstruction of fluorophore orientations based on all intensity
    data shown in Fig. 1. Orientations are shown as short lines only in voxels
    whose fluorescence intensities surpassed a threshold. To highlight the two
    sets of actin bundles discussed in the caption of Fig. 1, we split the
    volume with a plane and colored the proximal voxels red and the distal
    voxels green. The reconstructed orientations approximately align with the
    long axes of the actin filaments as expected.
\end{minipage}
 \vspace{-1em}
{\footnotesize\bibliography{abstract}{}}
\bibliographystyle{osajnl}
